---
title: "Reproducible Pitch Presentation"
author: "Victor Latorre Garrido"
date: "31/5/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, comment = NA)
```


## Work Presentation
- This is the final presentation for the Developing Data Products course inside the Data Scientist Specialization from the John Hopkins University (Coursera).

- The shiny application which have been developed, helps initially to understand how kmeans clustering performs (graphically) over the iris dataset depending on the number of clusters selected.

## Iris Data Set presentation

- Some statistics over the variables in the iris datasets are presented:

```{r iris, echo = TRUE}
summary(iris)
```

## Slide with R Output

- You can access to the shinny application throug the following link:

<https://victorlatorregarrido.shinyapps.io/IrisClustering/>

- Changing the number k in the slider input, you will obtain the representation on some visualizations of the iris data of the clustering result.


## Slide with Plot

- The following result corresponds to the best selection for k for the iris dataset:

```{r pressure}
iris.new<- iris[,c(1,2,3,4)]
iris.class<- iris[,"Species"]

normalize <- function(x){
    return ((x-min(x))/(max(x)-min(x)))
}
        
iris.new$Sepal.Length<- normalize(iris.new$Sepal.Length)
iris.new$Sepal.Width<- normalize(iris.new$Sepal.Width)
iris.new$Petal.Length<- normalize(iris.new$Petal.Length)
iris.new$Petal.Width<- normalize(iris.new$Petal.Width)
        
result <- kmeans(iris.new, 3)
        
  
plot(iris.new[c(1,2)], col=result$cluster)
```

